Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
added ntk stuff to discussion

>>>>

It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
